\textbf{Are regime changes always bad economics? Evidence from daily financial data}

### 2023-05-17 doc/regime_changes_bp_rr.tex
Add eGarch and tGarch volatility estimates

%\setcounter{tocdepth}{1}
\begin{document}
\author{Devin Incerti\thanks{Independent researcher. devin.incerti@gmail.com} and Trevor Incerti\thanks{Corresponding author. Assistant Professor, Department of Political Science, University of Amsterdam.  t.n.incerti@uva.nl.}}
\title{\textbf{Are regime changes always bad economics? Evidence from daily financial data \thanks{We are grateful to Peter Aronow, Matthew Graham, and Frances Rosenbluth for helpful feedback and suggestions. Authors are listed in alphabetic order, implying equal authorship. Any and all errors are our own.}}}
\date{\today}
\maketitle
\thispagestyle{empty}

@@

>>>>

%\setcounter{tocdepth}{1}
\begin{document}
\author{Devin Incerti\thanks{Independent researcher. devin.incerti@gmail.com} and Trevor Incerti\thanks{Corresponding author. Assistant Professor, Department of Political Science, University of Amsterdam.  t.n.incerti@uva.nl.}}
\title{\textbf{Are regime changes always bad economics? Evidence from daily financial data \thanks{We are grateful to P.M. Aronow, Matthew Graham, Frances Rosenbluth, and four anonymous reviewers for helpful feedback and suggestions. Authors are listed in alphabetic order, implying equal authorship. Any and all errors are our own.}}}
\date{\today}
\maketitle
\thispagestyle{empty}

@@

\begin{figure}[H]
\includegraphics[scale = 0.75]{../figs/mean-volatility-egarch.pdf}
\caption{Mean of volatility estimates from exponential GARCH models}
\label{fig:volatility}
\end{figure}

\begin{figure}[H]
\includegraphics[scale = 0.75]{../figs/mean-volatility-tgarch.pdf}
\caption{Mean of volatility estimates from threshold GARCH models}
\label{fig:volatility}
\end{figure}
